%-----------------
% Library Contents
%-----------------

\section*{Library overview}
  \label{library-contents}

  The scikit-image project started in August of 2009 and has received contributions from more than 100 individuals\footnote{\url{https://www.ohloh.net/p/scikit-image}}.  The package can be installed on all major platforms (e.g. BSD, GNU/Linux, OS X, Windows) from, amongst other sources, the Python Package Index (PyPI)\footnote{\url{http://pypi.python.org}}, Continuum Analytics Anaconda\footnote{\url{https://store.continuum.io/cshop/anaconda}}, Enthought Canopy\footnote{\url{https://www.enthought.com/products/canopy}}, Python(x,y)\footnote{\url{https://code.google.com/p/pythonxy}}, NeuroDebian \citep{neurodebian} and GNU/Linux distributions such as Ubuntu\footnote{\url{http://packages.ubuntu.com}}. In March 2014 alone, the package was downloaded more than 5000 times from PyPI\footnote{\url{http://pypi.python.org/pypi/scikit-image}, Accessed 2014-03-30}.

  As of version 0.10, the package contains the following sub-modules:

  \begin{itemize}

    \item color: Color space conversion.
    \item data: Test images and example data.
    \item draw: Drawing primitives (lines, text, etc.) that operate on NumPy arrays.
    \item exposure: Image intensity adjustment, e.g., histogram equalization, etc.
    \item feature: Feature detection and extraction, e.g., texture analysis, corners, etc.
    \item filter: Sharpening, edge finding, rank filters, thresholding, etc.
    \item graph: Graph-theoretic operations, e.g., shortest paths.
    \item io: Wraps various libraries for reading, saving, and displaying images and video, such as Pillow\footnote{\url{http://pillow.readthedocs.org/en/latest/}, Accessed 2015-05-30} and FreeImage\footnote{\url{http://freeimage.sourceforge.net/}, Accessed 2015-05-15}.
    \item measure: Measurement of image properties, e.g., similarity and contours.
    \item morphology: Morphological operations, e.g., opening or skeletonization.
    \item novice: Simplified interface for teaching purposes.
    \item restoration: Restoration algorithms, e.g., deconvolution algorithms, denoising, etc.
    \item segmentation: Partitioning an image into multiple regions.
    \item transform: Geometric and other transforms, e.g., rotation or the Radon transform.
    \item viewer: A simple graphical user interface for visualizing results and exploring parameters.

  \end{itemize}

  For further details on each module, we refer readers to the API documentation
  online\footnote{\url{http://scikit-image.org/docs/dev/api/api.html}}.
